---
title: "Los Lagos Region, a systematic review"
author: "Giorgia Graells"
output:
  word_document:
    reference_docx: "Para_Template.docx"
bibliography: References.bib
---

```{r setup, error=FALSE, include=FALSE, results= FALSE }
knitr::opts_chunk$set(echo = FALSE, include=FALSE, comment=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(patchwork)
library(ggplot2)
```


```{r}
DF <- read_csv("WebScience_Ref.csv")
```

# Introduction

1. Establish importance of the fild- provide background, keywords- present the problem 
[Stablish the importance of this research topic]
Protected areas (PA) are one of the most effective elements to protect biodiversity. 

[Provide general background information]
However, future of biological and landscape conservation not only need planned increment in the number of PA, but also effectiveness in terms of strategic allocation of management and economic efforts [@le2013protected; @watson2014performance].

[Stablish the importance of this research topic, more specific/detailed way] 
This is why the last decades aspect as economic limitations and the impact on local stakeholders are been taking into account in order to decrate news PA and not only its selection based in ecological knowledge [@borrini2004indigenous, Brown, 2002?].

[Provide general background information, more specific/detailed way]
However, even ecological knowledge have needed the expnsion to different areas that resume its complexity in order to face calimate change


2. Previous and current research and contributions 
[Describe general problem area or the current research focus of the field] 

Sudamerica count with more relative % of PA , %  of the area are PA...
Chile has 211 PA in its extention including 187 of them with a national jurisdiction, 
and only 24 international (Ramsar Site, Wetland of International Importance, Biosphere Reserve, and UNESCO-MAB Biosphere Reserve ). 

Los Lagos region, is named given this region has the largest proportion of lake area in the country, with 52 lakes over 3Km2, and a total area of  	2.850 . It has a total of  828.708 of population (Censo 2017) and an extension of 48,583.60 Km2.
Los lagos region has 21 PA that includes 37,529 Km2 of surface [@ProtectedAreas].


Ecosistemas de chile: Luebert y Pliscoff (2017)

According to aichi these areas are.... 
however...
probably because...
basarse en esta parte:
-PA intervenes with growing economic activities : This region presents one of the bigest growth in fisheries an acuacultere growth in comparision qwith the rest of the country during the last 30 years [@Soto-alvaradoDesarrollo]. Importantes actividades económicas se desarrollan en Los Lagos, en actividades principalmente vinculadas al sector primario de la economía: la ganadería, la acuicultura, la industria forestal [@BNC_LosLagos]
as most of the PA these areas are located in remoted places, 
la integración entre áreas protegidas y comunidades locales no ha demostrado ser del todo exitosa (Brown, 2002).
Local communities can present conflicts with PA because 1. they depend on the resources and some PA reinforce strict conservation (Brown, 2002), 2. there are not conection with Pa making that sorruended communities do not have, in most of the cases, nexux with the territory (Joppa & Pfaff, 2009- por areas remotas), or 
cuatro de las seis categorías de áreas protegidas de la Unión Internacional para la Conservación de la Naturaleza (UICN) refuerzan la conservación estricta, debido a que al interior de las áreas protegidas sólo está permitido el uso no consuntivo de los recursos naturales (Brown, 2002). 
Most of the protected areas area located in remoted places what improve protection. However, being away of develped urban centers (centros de desarrollo de la sociedad actual ) makes that sorruended communities to protected areas do not have, in most of the cases, nexux with the territory (Joppa & Pfaff, 2009) ))

This presents a disconection betwwen local communities
Sin embargo, esto tambien conlleva al desconocimineto de elementos que pueden ser claves por falta de investigaciones
tambien los problemas que conllevva a las comunidades el abandono or parte de las autoridades.
    




[Provide transition between the general problem area and the literature review]
this area sustain xx protected areas: xx National Parks, xx National Reserves, and xx others
Three of those are andean national parks: Puyehue National Park (PNP), Vicente Perez Rozales National Park (VPRNP), Alerce Andino national park (AANP). 



3. Locate the gap-describe the proble to address-present a prediction to be tested 

[Provide brief overview of key research projects in this area]

PNP, VPRNP, and AANP as all national PA in Chile are under the supervision and adminstration of the National Forestry Corporation CONAF). They count with management plans (2008, 2015, and 1997, respectibly), which provides a very carfull compilation of information, however they have not been correctly updated and lack of the changes that have occurred in the last years. For example, between 1995-2016 native forests in this area have suffer important losses because of land use changes (mostly land modification to grassland and shrubs, and substitution) (Marquet P. A., A. Altamirano, M. T. K. Arroyo, M. Fernández, S. Gelcich, K.  Górski,  E.  Habit,  A.  Lara,  A.  Maass,  A.  Pauchard,  P.  Pliscoff,  H.  Samaniego y C. Smith-Ramírez (editores) (2019). Biodiversidad y cambio climático en Chile: Evidencia científica para la toma de decisiones. Informe de   la   mesa   de   Biodiversidad.   Santiago:   Comité   Científico   COP25; Ministerio de Ciencia, Tecnología, Conocimiento e Innovación.).

[Describe gaps in the research] 

Considering this area presents an increment of vulnerability in front of climate change, there is a need to incorporate different components of ecological knowledge as well the interaction with local communities in these PA in order to generete projections of climate chage to develop corservation plans to the future.


[Decribe paper itself]
This review revist the ecological literature carry out in these three protected areas and its surroundings in Los lagos Region in order to generate a base line that allow to proyect scenarios of climate change to systematic conservation planning in PA.

4. Describe the present paper 
[Give details about the methodology reported in the paper]
We made a systematic review of research in the Web of Knowledge database in two parts:1. searching by the names of the three PA:PNP, VPRNP, and AANP, and 2. serching by the greographical area of Southern Chile.

[Announces the findings]
We identified tendencies and gaps in research developed in these three National Parks, and a vision on where to focus new studies that allow systematic conservation plans that includes xx to deal with climate change and ensure the biodiversity in southern Chile.

incluir: possibility to generate a methodology to include climate Change into PAs planning, from their creation to their management and administration, assessing their value as well as their vulnerabilities at landscape scales


# Methodology

1. Overview-purpose of the work-give source of material/equipment used 
[General overview of this section]

In order to identify research developed in the focus area, a systematic review of literature was performed through the Web of Science database. Information was categorized according to research areas presented in this project.

[Provide background information and justification]
We focus our systematic review geographicaly in the Andes mountain chain and central vally, and not coastal mountain chain and coast.




[Provide an overview of the procedure/method itself]

Two eligibility criteria were performed: 1. including the name of the National Parks of interes, using keywords at topic level: "Puyehue National Park" or "Vicente Perez Rozales National Park" or "Alerce Andino National Park", and 2. Geographic areas surrounding the National Parks, using keywords at topic level: "South Central Chile" or "North Chilean Patagonia" or "Los Lagos Region". The period of the search included from 1975 until October 2020. Selection of articles followed prisma flow diagram. Grey-literature was not incorporated in the selection.



2. Details about materials and methods- justify choices 
[Provide details about what was done and used and shows that care was taken] 

Articles selected were categorized by publication year, source title, keywords used, area of study, study location, objective, methodology, process, and study object. 



[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]

Area of study included Ecosystem functioning and services, Freshwater biodiversity, Hydrology, Social-ecological, and also complementary areas such as Arqueological, Biogeography, Climate, Environmental conditions, Exotic species, Paleoecology, Seismiology, and Species description.

Study location encompas categories such as AANP, PNP, and  VPRNP, group by National Parks;  Adjacent to AANP, Adjacent to PNP, Adjacent to VPRNP, Andes of Los Rios Region, and Neuquen, Argentina  group by similar ecosystems; Los Rios region, 2 regions, 3 regions, 4 regions,  5 regions, More than 5 regions, Chile, Chile and Argentina, group by larger areas including the NP; Los Lagos Region, Valdivia group by close to NP but not same ecosystem. 

Methodology classified according to how data was obtain

The category called proccess implies biological, ecological or physical  

3. Relate to other studies 
[Describe what was done by referring to existing mehods in the literature] 
We focus our findings in Los lagos región research and andean studies, leaving out coastal systems and in particular Chiloe island.


[Provide more detailed information about the method and show that was a good choice]

4. Indicate where problems occurred 

[Mention possible difficulty in the methodology]

# Results

1. Revisting the research aim/existing research


2. General overview of results

A total of  `r nrow(DF)` articles were selected in this review.

```{r}
# From those ` r DF %>% dplyr::filter(`Keywords used`=="Name of parks") %>% nrow()` articles were find from National parks names searching and ` r DF %>% dplyr::filter(`Keywords used` =="Close area") %>%  nrow()` articles from searching nearby areas od the parks. 
```

3. Invitations to view results
In general terms, articles have been growing in number, however there are years that clearly show a decline in publications (Fig 1). 


```{r}
Pub_year <-ggplot(DF) + geom_bar(aes(x = `Publication Year`))+  labs(y="Number of articles", x="Publication year")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))
Pub_year
```

### References