---
title: "Review_Ms. Todo menos figuras"
author: "Giorgia Graells"
output:
  bookdown::word_document2:
    reference_docx: "Para_Template.docx"
bibliography: References.bib
---

```{r setup}
knitr::opts_chunk$set(echo = FALSE, include=FALSE, comment=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(patchwork)
library(ggplot2)
```


```{r}
DF <- read_csv("WebScience_Ref.csv")
```

# Introduction

1. Establish importance of the fild- provide background, keywords- present the problem 
[Stablish the importance of this research topic]
Protected areas (PA) are one of the most effective elements to protect biodiversity. 

[Provide general background information]
However, future of biological and landscape conservation not only need planned increment in the number of PA, but also effectiveness in terms of strategic allocation of management and economic efforts [@le2013protected; @watson2014performance].

[Stablish the importance of this research topic, more specific/detailed way] 
This is why the last decades aspect as economic limitations and the impact on local stakeholders are been taking into account in order to decrate news PA and not only its selection based in ecological knowledge [@borrini2004indigenous, Brown, 2002?].

[Provide general background information, more specific/detailed way]
However, even ecological knowledge have needed the expnsion to different areas that resume its complexity in order to face calimate change


2. Previous and current research and contributions 
[Describe general problem area or the current research focus of the field] 

Sudamerica count with more relative % of PA , %  of the area are PA...

Chile has xxx Pa in its extention. However, as most of the PA these areas are located in remoted places, 

Local communities can present conflicts with PA because 1. they depend on the resources and some PA reinforce strict conservation (Brown, 2002), 2. there are not conection with Pa making that sorruended communities do not have, in most of the cases, nexux with the territory (Joppa & Pfaff, 2009- por areas remotas creo).

makes  or they depend on them 

Los lagos region, is named given there aer more than xx lakes in its area.
This region presents one of the bigest growth in fisheries an acuacultere growth in comparision qwith the rest of the country during the last 30 years [@Soto-alvaradoDesarrollo].
Ecosistemas de chile: Luebert y Pliscoff (2017)
la integración entre áreas protegidas y comunidades locales no ha demostrado ser del todo exitosa (Brown, 2002).






WPADB

 Sin embargo, 
metas aichi

cuatro de las seis categorías de áreas protegidas de la Unión Internacional para la Conservación de la Naturaleza (UICN) refuerzan la conservación estricta, debido a que al interior de las áreas protegidas sólo está permitido el uso no consuntivo de los recursos naturales (Brown, 2002). 


Most of the protected areas area located in remoted places what improve protection. However, being away of develped urban centers (centros de desarrollo de la sociedad actual ) makes that sorruended communities to protected areas do not have, in most of the cases, nexux with the territory (Joppa & Pfaff, 2009) 

This presents a disconection betwwen local communities
Sin embargo, esto tambien conlleva al desconocimineto de elementos que pueden ser claves por falta de investigaciones
tambien los problemas que conllevva a las comunidades el abandono or parte de las autoridades.
    




[Provide transition between the general problem area and the literature review]
this area sustain xx protected areas: xx National Parks, xx National Reserves, and xx others
Protected areas as xx and xx area under the supervision of the National Forestry Corporation or CONAF. 
Three of those are andean national parks: Puyehue National Park (PNP), Vicente Perez Rozales National Park (VPRNP), Alerce Andino national park (AANP). 

The ecosystems in this area have been modified by continuos natural evvents such as volcanic activity and earthquakes.
Active Andean volcanism [@SternVolcanism]. Among the larger, more active and/or better known volcanic centers in the SVZ are: Puyehue (2,240 m in PNP), Cordón Caulle (2,236 m; in PNP), Tronador (3,565 m; in VPRNP), Osorno (2,661 m; López-Escober et al., 1992; Petit-Breuilh, 1999), Calbuco (2,015 m; in RNL)
earthquake 1960 en valdivia (https://www.nature.com/articles/s41467-018-05989-6)




- carbon emision in near cities and woodplaces dependencies high level of pollution

Even multiple sites have showed obsidian sources and distribution in Patagonia. (http://geode.colorado.edu/~geolsci/facultyweb/sternpdf/stern%202017%20Obsidian%20in%20Patagonia%20Quat%20International.pdf)
Obsidian it is an extrusive igneus rock and is signal of volcanic activiy area. This rock was valued by old cultures, fractured and used as arrowheads.

como registros de tephra










3. Locate the gap-describe the proble to address-present a prediction to be tested 

[Provide brief overview of key research projects in this area]

Even when there is research carry out in natural areas in southern Chile, there is not projections of climate chage in order to corservation planning to the future of protected areas
hasta donde estas areas serán capaces de proteger a las especies en el futuro considderando el cambio climatico y la respuesta de las distintass especies

dificultad de proyeccion, los planes son antiguos (VPRNP 2015, PNP 2008, AANP 1997)


[Describe gaps in the research] 
Necesidad de concoer el presente para proyectar el futuro
There are two
that area particularly important in the context of the present proposal: 1) The need to improve our
knowledge on the consequences of climate change on freshwater ecosystems, integrating biodiversity
dimension with hydrological ones, and 2) the importance of monitoring and adequately include climate
change into the PAs managing plans. Both aspects were included in the updated NDC of Chile, so there is
explicit national commitment to tackle both recommendations.

[Decribe paper itself]
This review revist the ecological literature carry out in these three protected areas and its surroundings in Los lagos Region in order to generate a bese line that allow to proyect scenarios of climate change to systematic conservation planning in PA

4. Describe the present paper 
[Give details about the methodology reported in the paper]
We made a systematic review of research in the Web of Knowledge database in two parts: searching by the names of the national parks (elegidos para este trabajo) and a broader area of Southern Chile.

[Announces the findings]
The results helped to understand focussed areas of studied and those in which more research is needed.


aim: as a concrete possibility to generate a methodology to include climate Change into PAs planning, from their creation to their management and administration, assessing their value as well as their
vulnerabilities at landscape scales
Aunque sudamerica posee un gran porcentaje de pa, es necesario identificar el tipo de investigaciones que estas ha reunido para definir sus tendencias, gaps y ver hacia donde apuntar para poder desarrollar herramientas que permitan generar una correcta planificacion systematica que incluya todas la reas necesarias (o la mayoria) para enfrentarnos al cambio climatico y poder resguardar la biodiversidad biologica del sur de CHile.

 building  systematic  planning  process

# Methodology

1. Overview-purpose of the work-give source of material/equipment used 
[General overview of this section]

In order to identify research developed in the focus area, a systematic review of literature was performed through the Web of Science database. Information was categorized according to research areas presented in this project.

[Provide background information and justification]
Will focus our systematic review geographicaly in the Andes mountain chain and central vally, and not coastal mountain chain and coast.




[Provide an overview of the procedure/method itself]

Two eligibility criteria were performed: 1. including the name of the National Parks of interes, using keywords at topic level: "Puyehue National Park" or "Vicente Perez Rozales National Park" or "Alerce Andino National Park", and 2. Geographic areas surrounding the National Parks, using keywords at topic level: "South Central Chile" or "North Chilean Patagonia" or "Los Lagos Region". The period of the search included from 1975 until October 2020. Selection of articles followed prisma flow diagram. Grey-literature was not incorporated in the selection.



2. Details about materials and methods- justify choices 
[Provide details about what was done and used and shows that care was taken] 

Articles selected were categorized by publication year, source title, keywords used, area of study, study location, objective, methodology, process, and study object. 



[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]

Area of study included Ecosystem functioning and services, Freshwater biodiversity, Hydrology, Social-ecological, and also complementary areas such as Arqueological, Biogeography, Climate, Environmental conditions, Exotic species, Paleoecology, Seismiology, and Species description.

Study location encompas categories such as AANP, PNP, and  VPRNP, group by National Parks;  Adjacent to AANP, Adjacent to PNP, Adjacent to VPRNP, Andes of Los Rios Region, and Neuquen, Argentina  group by similar ecosystems; Los Rios region, 2 regions, 3 regions, 4 regions,  5 regions, More than 5 regions, Chile, Chile and Argentina, group by larger areas including the NP; Los Lagos Region, Valdivia group by close to NP but not same ecosystem. 

Methodology classified according to how data was obtain

The category called proccess implies biological, ecological or physical  

3. Relate to other studies 
[Describe what was done by referring to existing mehods in the literature] 
We focus our findings in Los lagos región research and andean studies, leaving out coastal systems and in particular Chiloe island.


[Provide more detailed information about the method and show that was a good choice]

4. Indicate where problems occurred 

[Mention possible difficulty in the methodology]

    
# Results

1. Revisting the research aim/existing research


2. General overview of results

A total of  `r nrow(DF)` articles were selected in this review. From those ` r DF %>% dplyr::filter(`Keywords used`=="Name of parks") %>% nrow()` articles were find from National parks names searching and ` r DF %>% dplyr::filter(`Keywords used` =="Close area") %>%  nrow()` articles from searching nearby areas od the parks. 

3. Invitations to view results
In general terms, articles have been growing in number, however there are years that clearly show a decline in publications (Fig \@ref(fig: Years)). 


```{r Years}
Pub_year <-ggplot(DF) + geom_bar(aes(x = `Publication Year`))+  labs(y="Number of articles", x="Publication year")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))
Pub_year
```






From the total of articles, only ` r ((DF %>% dplyr::filter(`Study location` %in% c("AANP", "PNP", "VPRNP")) %>% nrow())/nrow(DF))*100`% (Fig \@ref(fig: Locations)), where ` r DF %>% dplyr::filter(`Study location` == "PNP") %>% nrow()` articles were carry out in PNP, and only ` r DF %>% dplyr::filter(`Study location` == "AAPN") %>% nrow()` in AAPN and ` r DF %>% dplyr::filter(`Study location` == "VPRPN") %>% nrow()` in VPRPN.  Adjacents areas to NP comprehended a ` r ((DF %>% dplyr::filter(`Study location` %in%  c("Adjacent to PNP", "Adjacent to AANP", "Adjacent to VPRNP") %>% nrow())/nrow(DF))*100`% of the studies. 

```{r Locations}
DF_Location <- DF %>%  group_by(`Study location`) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(`Study location`)) %>% 
  mutate(`Study location`=fct_reorder(`Study location`, -n))

DF_Location2 <- DF_Location %>% 
  mutate(`Study zone`= case_when(`Study location` %in% c("3 regions", "4 regions", "5 regions", "More than 5 regions")~"Various regions of Chile",  `Study location` %in% c("PNP", "AANP", "VPRNP")~"National Parks", `Study location` %in% c("Adjacent to PNP", "Adjacent to AANP", "Adjacent to VPRNP")~"Adjacent areas to NP", `Study location` %in% c("2 regions", "Andes of Los Rios Region", "Neuquen, Argentina", "Argentinian andes")~"Similar ecosystems", `Study location` %in% c("Los Lagos Region")~"Larger areas that comprise the NP", `Study location` %in% c("Chile", "Chile and Argentina")~"Global studies")) %>%
  mutate(`Study zone`= str_wrap(`Study zone`, 15))
                                
Location2 <-ggplot(DF_Location2, aes(x = fct_reorder(`Study zone`,n, .desc=TRUE), y = n, group = `Study location`)) + geom_col(aes(fill=`Study zone`), position="dodge", color="black") + geom_text(aes(label = `Study location`), size=4, position=position_dodge(0.9), angle=90,vjust=0.5, hjust=-0.04 ) + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,66))+theme(legend.position = "none")+ scale_fill_brewer(palette = "Dark2") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
Location2
```


Most of the study areas ar mention in less than 20 articles in this revision, however ecosystem functionning and services highlights with its number of articles published ` r ((DF %>% dplyr::filter(`Area of study`=="Ecosystem functioning and services") %>% nrow() )/nrow(DF) )*100` % of the total (Fig \@ref(fig: Areas)). Ecosystem functionning and services has been studied in the three NP, however its proportion in PNP is notably higher than the other NP.

```{r Areas, fig.height=10, fig.width=8}
DF_Area <- DF %>% 
  mutate(`Area of study2`= case_when(`Area of study` %in% c("Arqueological","Paleoecology" )~"Archaeology and Paleoecology",
                                          `Area of study` %in% c("Climate","Environmental conditions", "Seismiology" )~ "Climate and environment",
                                          `Area of study` %in% c("Biogeography","Species", "Exotic species" )~ "Species and distribution",
                                         `Area of study` %in%  "Ecosystem functioning and services" ~ "Ecosystem func. & servic.",
                                          `Area of study` %in% "Freshwater biodiversity" ~ "Freshwater biodiversity",
                                          `Area of study` %in% "Hydrology" ~ "Hydrology",
                                          `Area of study` %in% "Social-ecological" ~ "Social-ecology")) %>% 
  mutate(`Area of study2`= str_wrap(`Area of study2`, 15)) %>% 
  group_by(`Area of study2`) %>% summarise(n = n()) %>% ungroup() %>%
   dplyr::filter(!is.na(`Area of study2`))

p1 <-ggplot(DF_Area) + geom_col(aes(x = fct_reorder(`Area of study2`, desc(n)), y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle =90, vjust = 0.5, hjust=1)) 


DF_Area2 <- DF %>% dplyr::filter(`Study location` %in% c("PNP", "VPRNP", "AANP")) %>% 
   mutate(`Area of study2`= case_when(`Area of study` %in% c("Arqueological","Paleoecology" )~"Archaeology and Paleoecology",
                                          `Area of study` %in% c("Climate","Environmental conditions", "Seismiology" )~ "Climate and environment",
                                          `Area of study` %in% c("Biogeography","Species", "Exotic species" )~ "Species and distribution",
                                         `Area of study` %in%  "Ecosystem functioning and services" ~ "Ecosystem func. & servic.",
                                          `Area of study` %in% "Freshwater biodiversity" ~ "Freshwater biodiversity",
                                          `Area of study` %in% "Hydrology" ~ "Hydrology",
                                          `Area of study` %in% "Social-ecological" ~ "Social-ecology")) %>% 
  mutate(`Area of study2`= str_wrap(`Area of study2`, 15)) %>% 
  group_by(`Area of study2`, `Study location`) %>% summarise(n = n()) %>% ungroup() %>%
   dplyr::filter(!is.na(`Area of study2`))
  

p2 <- ggplot(DF_Area2) + geom_col(aes(x = fct_reorder(`Area of study2`, desc(n)), y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + facet_wrap(~`Study location`, scales="free_x")

p1/p2
```


Data collected form the field is abundant  ` r ((DF %>% dplyr::filter(`Mehodology` %in% c("Field survey", "Field collection", "Field experiment")) %>% nrow() )/nrow(DF) )*100` % (Fig \@ref(fig: Areas)).

```{r}
DF <- DF %>% 
  mutate(General_methods= case_when(
    Methodology %in% c("Field collection", "dendrochronology", "Electric fishing")~"Field collection",  
    Methodology %in% c("Field survey", "Sampling stations")~"Field survey", 
    Methodology %in% c("Field experiment", "Transplant experiment", "Seedling experiment", "Stratigraphy")~"Field experiment", 
    Methodology %in% c("Communicational strategy", "Discussion", "Quantitative and qualitative methods", "Survey", "Interview")~"Social methods", 
    Methodology %in% c("Correlations","Modeling", "Multivariate model", "Remote sensing","Simulations", "spatially explicit model")~"Modeling", 
    Methodology %in% c("Chile", "Chile and Argentina")~"Global studies",
    Methodology %in% c("Isotopes","Genetic analysis", "Reconstruction of mtDNA")~"Molecular analysis",
    Methodology %in% c("Review of literature")~"Review of literature"))

DF_Methodology <- DF %>%  group_by(Methodology, General_methods) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(Methodology)) %>% mutate(Methodology=fct_reorder(Methodology, -n)) %>% mutate(General_methods= str_wrap(General_methods, 16))


p1 <-ggplot(DF_Methodology, aes(x = fct_reorder(General_methods, n, .desc=TRUE), y = n, group = Methodology)) + geom_col(aes(fill=General_methods), position="dodge", color="black") + geom_text(aes(label =Methodology), size=4, position=position_dodge(0.9), angle=90,vjust=0.5, hjust=-0.04 ) + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,66))+theme(legend.position = "none")+ scale_fill_brewer(palette = "Dark2") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
p1


```
Field collection included mehods sucha asdendrochronology, electric fishing.


Modeling category included correlational, multivariete , and spatially explicit models





```{r}
DF_object <- DF %>%  group_by(`Study object`) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(`Study object`)) %>% mutate(`Study object`=fct_reorder(`Study object`, -n))

DF_object <- DF_object %>% 
  mutate(General_object= case_when(
    `Study object` %in% c("People", "Urban areas")~"Human",  
    `Study object` %in% c("Aegorhinus", "Austrocedrus", "Bird species","Chusquea", "Craspedacusta","Didymosphenia", "Dromiciops", "F. cupressoides", "Lichen", "Nothofagus",   "Salmonids", "Liolaemus", "Wild boar")~"Species", 
    `Study object` %in% c( "Groundwater Storage", "Lakes", "runoff", "Soil","Streams", "watershed")~"Geographic elements", 
    `Study object` %in% c("Forest","Native forest")~"Ecosystem",
    `Study object` %in% c("Fires","Particulate matter","Precipitation", "Rock art")~"Physical conditions",
    `Study object` %in% c("Aquatic plants" )~"Group of plants",
    `Study object` %in% c("Bird species","Fishes","Crustacean", "Evergreen trees", "Nothofagus")~"Communities")) %>%
  mutate(General_object= str_wrap(General_object, 18))


p1 <-ggplot(DF_object, aes(x = fct_reorder(General_object, n, .desc=TRUE), y = n, group = `Study object`)) + geom_col(aes(fill=General_object), position="dodge", color="black") + geom_text(aes(label =`Study object`), size=4, position=position_dodge(0.9), angle=90,vjust=0.5, hjust=-0.04 ) + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,66))+theme(legend.position = "none")+ scale_fill_brewer(palette = "Dark2") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
p1


```


4. Specific/key results in details


## Hydrology

From the total of articles centered on hydrology, 

```{r Hydrology, fig.height=9}
DF_Hydro <- DF %>%  group_by(`Area of study`, Process, General_methods, `Study object`) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(`Area of study`== "Hydrology")
#%>% mutate(`Area of study`= str_wrap(`Area of study`, 24)) %>% dplyr::filter(!is.na(`Area of study`))

Hydro1 <- ggplot(DF_Hydro) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Hydro2 <- ggplot(DF_Hydro) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Hydro3 <- ggplot(DF_Hydro) + geom_col(aes(x = `Study object`, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5)) 
(Hydro1 + Hydro2)/Hydro3
```

Spectral characterrization and comparison among lakes in @delosRiosSpectral
We show that annual runoffis highly sensitive to the relative area of FPto NF: ratios of FP to NF areas of 10%, 50% and 90% would lead to 3%,−18% and−40% changes inmean annual runoff, respectively.(Alvarez-Garreton et al 2019)



## Ecosystem functioning and services

Field collection methods registered in ecosystem functioning and services included activities such as dendrochronological samples, 
Field surveys methods area a lot
Field experiment methods included seedling and transplant experiments.



```{r Ecosys, fig.height=12}
DF_Ecosys <- DF %>%  group_by(`Area of study`, Process, General_methods, `Study object`) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(`Area of study`== "Ecosystem functioning and services")
#%>% mutate(`Area of study`= str_wrap(`Area of study`, 24)) %>% dplyr::filter(!is.na(`Area of study`))

Ecosys1 <- ggplot(DF_Ecosys) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Ecosys2 <- ggplot(DF_Ecosys) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Ecosys3 <- ggplot(DF_Ecosys) + geom_col(aes(x = `Study object`, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
(Ecosys1 + Ecosys2)/Ecosys3
```

Chusquea fenology in @delaFuenteChusquea 
El área de estudio se ubica en el sector de Antillanca (40º78’S y 72º22’O,

Improvements for the study of volcanic activity [@AmoebaeTephra]

Steam radious of F. cupressoides and the determination of environmental variables that affect its growth... with projections in climate change [@Stem_F]

SUcculence in rain forest [@GodoySucculence]
Key results – We show that leaves from sun conditions, the environment with higher water demand, have lower SLA (specific leaf area), thicker epidermis and store more water due to a thicker spongy parenchyma, than leaves from shade conditions. Conclusions  –  We  found  high  phenotypic  variation  in  S.  repens at intraspecific level in response to contrasting environmental conditions. This variation reflects a two-fold strategy common in epiphytes: increase water storage and reduce water loss. Furthermore, it suggests that leaf succulence has an adaptive value even in a temperate cold rainforest. We discuss that the occurrence of succulence on a cold rainforest might be explained by a combination of ecological, biogeographic and phylogenetic factors.

macropytes  and  riparian  assemblages  are  not  random,  that means  that  the  regulator  factors  are  deterministic. 


They reconstructed stand development on sites affected by these disturbances (complex mosaic of disturbance patterns, including the effects of the strong 1960 earthquake as well as fire and wind disturbance), and compared these patterns with the structure of old-growth forests along an elevation gradient from species-rich montane rain forest to mono-typic subalpine Nothofagusforests


## Social-ecological
Socio-ecological research included quantitative and qualitative social methods which includes people's surveys, interviews and articles of discission based on etnography.


```{r Social, fig.height=9}
DF_Social <- DF %>%  group_by(`Area of study`, Process, General_methods, `Study object`) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(`Area of study`== "Social-ecological")
#%>% mutate(`Area of study`= str_wrap(`Area of study`, 24)) %>% dplyr::filter(!is.na(`Area of study`))

Social1 <- ggplot(DF_Social) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Social2 <- ggplot(DF_Social) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Social3 <- ggplot(DF_Social) + geom_col(aes(x = `Study object`, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5)) 
(Social1 + Social2)/Social3
```

Turism and peoples movement in @SozaAmigoTurism

conection with PNP with thre cities valdivia, Osorno y Puerto Montt (154.716, 147.826, and 220.143 of urban population respectibly, according to 2017 Census, Chile )
The results show that the chang-es in the economic structure had improve the main sectors of the centers, weakening the potential development of the Park. Especially the lacks of connectivity development and the small supply of good and services of the Park are the main constraint that arise from the analysis to increase the number and length of visits. 


Social actors in AANP and LLNR buffer in @mardones_social

The study was focused in the buffer zone 
El estudio combina el análisis cualitativo del mapeo de actores (MDA) con el mé-todo cuantitativo del análisis de redes sociales (ARS).
La inves-tigación utiliza una aproximación sociométrica al análisis de redes sociales, el cual se refiere al estudio de las propiedades estructurales de una red, tales como densidad y cohesión (Marín, Gelcich, Castilla, & Berkes, 2012). 
Social studies mention haigh fragmentations of social network according to economic sectors (agriculture, artisal fisheries, turism, among others ). 
Low participation and separation from the protected area which has not incorporated the community 


## Freshwater biodiversity

Field collection methods registered in freshwater biodiversity included activities such as electric fishing and sampling stations.

```{r Fresh, fig.height=9}
DF_Fresh <- DF %>%  group_by(`Area of study`, Process, General_methods, `Study object`) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(`Area of study`== "Freshwater biodiversity")
#%>% mutate(`Area of study`= str_wrap(`Area of study`, 24)) %>% dplyr::filter(!is.na(`Area of study`))

Fresh1 <- ggplot(DF_Fresh) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Fresh2 <- ggplot(DF_Fresh) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Fresh3 <- ggplot(DF_Fresh) + geom_col(aes(x = `Study object`, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5)) 
(Fresh1 + Fresh2)/Fresh3
```


## Conservation priorization -Climate change

5. Comparisons with results in other research
6. problems with results
7. Possible implications with results




# Discussion 

1. Revisting previous research- summarise 
[Revisit previous research] 
A large number of articles centred in southern Chile are focossed in perturbations in that area of study. This studies mention aspects as volcanic activities, siesmology

[Revisit Introduction to recall specific weakness in methodology used in previous studies]

2. Mapping 
[Revisit methodology used in this study] 
Review of literature in 

[Revisit and summarise the results] 
COMO LLAMA PABLO A LAS AREAS DE ESTUDIO?

[Show where and how the present work fits into the research “map” in this field]

3. Achivements/contributions- refining implications 
[Recall an aspect of the results that represents a postitive achievement or contribution of this work] 
This review allow to recognize the studies carry out in these three national parks and the research in the area in theirs surroundings
we found that most research are focused in native forest regeneration, groth and succession, showing a bias in forestry potential of native forest

[Focus in the meaning and implications of the achievements in this work]


[Note if one of the achievement or contributions of the work is a novelty] 

[Describe implications of the results, including possible applications]
These knowledge allow to generate a baseline to work in the future

4. Limitations-current and future work-applications 
[Describe limitations which should direct future research] 
The bias in ecosystem functioning and services limitate the develop in other areas

Furture research should be develop in those areas that are less studied

[Suggest a specific area to be addressed in future work]
Climate change scenarios


Latitudinal patterns in plant biodiversity [@BanisterLatitudinal] shows 
at 40°S there are more than 800 species, based on a bibliographic review of existing floristic studies at 2012.



 La estructura y composición homogénea de las plantaciones forestales promueven una mayor propagación del fuego en comparación con los bosques nativos deciduos de Nothofagus, que tienden a tener menor cantidad de incendios por presentar un combustible más heterogéneo y con mayor contenido de hu-medad (Gómez-González et al., 2019; McWethy et al., 2018). Dado que la principal fuente de ignición (>90%) de  los  incendios  forestales  en  Chile  se  asocia  con  la  actividad  humana  (accidental  o  intencional),  sectores  con vegetación más cercanos a centros poblados presentan mayor probabilidad de ocurrencia de incendios forestales (Gómez-González et al., 2019; McWethy et al., 2018). Los sectores más australes también han visto un incremento en incendios catastróficos. La particularidad de estos eventos es que suelen abarcar una su-perficie mucho mayor y generalmente afectan ecosistemas nativos, lo que por razones de acceso, topografía y  clima,  hacen  a  estos  incendios  muy  difíciles  de  controlar,  sumado  al  hecho  de  que  ocurren  en  zonas  con  escaso material para su combate oportuno. Acá podemos destacar los incendios en el Parque Nacional Torres del Paine en 2012 (cerca de 17.000 ha), Reserva Nacional China Muerta de 2015 (cerca de 3.700 ha) y Colonia Sur, Cochrane en 2019 (cerca de 15.000 ha).



There are just a few studies in hydrology in the region, although there are some more characterization including the valdivian forest [@LittleWatershed].

freshwater: we did not consider dideases in in chilean salmon industry [@RozasAmoebic]

Although we contemplate andean studies here, volcanic activity could create microhabitats more similar to areas in another region or with another climate ???
Remarkably consistent thermal state [@RotmanThermal]

plantas de embotrium y actividad volcanica [@DelgadoEmbothrium]
plant invasion in Climatic and socio-economic factors determine thelevel of invasion by alien plants in Chile [@FuentesInvasion]

Comparative morphology of annual shoots in seedlings of five Nothofagus species from Argentinian patagonia [@RaffaeleMorphology]

A Multiscale Method for AssessingVegetation Baseline of Environmental [@PauchardMultiscale]

Los Lagos es definida como una “Región sin Territorio, ya que las provincias que la forman (Osorno, Llanquihue, Chiloé y Palena) no comparten una noción común de territorio, ni menos una agenda regional común” (Montecinos, 2009, p. 24).
Modificacion de la actividad economica en la region producto de la entrada de la industria del salmon ha  generado un cambio cultural, donde predomina una dependdencia del mercado externo.

### References