---
title: "Review_Ms"
author: "Giorgia Graells"
output:
  bookdown::word_document2:
    reference_docx: "Para_Template.docx"
bibliography: References.bib
---

```{r setup, error=FALSE, include=FALSE, results= FALSE }
knitr::opts_chunk$set(echo = FALSE, comment=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(patchwork)
library(ggplot2)
```


```{r}
DF <- read_csv("WebScience_Ref.csv")
colnames(DF) <- make.names(colnames(DF))
```

```{r}
LosLagos <-read_csv("PACL_LL.csv")
```


# Introduction
Protected areas (PA) are one of the most effective elements to prevent extinctions hence conserve biological diversity. 
One of the strategic targets of the Convention of Biological Conservation is "By 2020, at least 17 per cent of terrestrial and inland water, and 10 per cent of coastal and marine areas, especially areas of particular importance for biodiversity and ecosystem services, are conserved through effectively and equitably managed, ecologically representative and well connected systems of protected areas..."
According to this, it has been a discussion about how future of biological and landscape conservation not only need planned increment in the number of PA, but also effectiveness in terms of strategic allocation of management and economic efforts [@le2013protected; @watson2014performance].
This is why the last decades aspect as economic limitations and the impact on local stakeholders are been taking into account in order to decrate news PA and not only its selection based in ecological knowledge [@borrini2004indigenous, Brown, 2002?].
However, even ecological knowledge have needed the expansion to different areas that resume its complexity in order to face climate change in the future.


Sudamerica counts with more relative % of PA , %  of the area are PA...
Chile has 211 PA in its extension, including 187 of them with national jurisdiction. There are only 24 PA international, incluiding two categories Ramsar Site, Wetland of International Importance and Biosphere Reserve, and UNESCO-MAB Biosphere Reserve. 
In southern Chile, Los Lagos Region is named given this region has the largest proportion of lakes area in the country, with 52 lakes over 3Km2, and a total area of	2.850 Km2. It has a population of 828.708 (Censo 2017) and an extension of 48,583.60 Km2.
This region bases its economy in activities related to primary sectors: livestock, aquiculture and forestry industry [@BNC_LosLagos]. Even more, Los lagos presents one of the bigest growth in fisheries an acuacultere growth in comparision with the rest of the country during the last 30 years [@Soto-alvaradoDesarrollo]. 

Los lagos region has 21 PA that includes 37,529 Km2 of surface [@ProtectedAreas]. From those,  `r LosLagos %>% dplyr::filter(DESIG %in% c("Monumento Natural", "Parque Nacional")) %>% nrow()` correspond to National parks and Natural Monuments which are IUCN categories that reinforce strict conservation (Brown, 2002). This addded to most of the PA are located in remote places, being away of develped urban centers. That makes sorrounded communities to PA do not have, in most of the cases, nexux with the territory (Joppa & Pfaff, 2009)
The integration between PAs and local communities it has not been smooth in southern Chile (Brown, 2002). However tourism has presented an poptunity to reconect the economy with nature since...

correspondeAccording to aichi these areas are.... 
This presents a disconection betwwen local communities
Sin embargo, esto tambien conlleva al desconocimineto de elementos que pueden ser claves por falta de investigaciones

[Provide transition between the general problem area and the literature review]

3. Locate the gap-describe the proble to address-present a prediction to be tested 

[Provide brief overview of key research projects in this area]
Los Lagos Region presents three Andean National Parks: Puyehue National Park (PNP), Vicente Perez Rozales National Park (VPRNP), and Alerce Andino National Park (AANP). PNP, VPRNP, and AANP as all national PA in Chile are under the supervision and adminstration of the National Forestry Corporation CONAF). They count with management plans (2008, 2015, and 1997, respectibly), which provides a very carfull compilation of information. However, thesedocuments have not been correctly updated and lack of the changes that have occurred in the last years. For example, between 1995-2016 native forests in this area have suffer important losses because of land use changes (mostly land modification to grassland and shrubs, and substitution) 
The area presents an increment of vulnerability in front of climate change (Marquet P. A., A. Altamirano, M. T. K. Arroyo, M. Fernández, S. Gelcich, K.  Górski,  E.  Habit,  A.  Lara,  A.  Maass,  A.  Pauchard,  P.  Pliscoff,  H.  Samaniego y C. Smith-Ramírez (editores) (2019). Biodiversidad y cambio climático en Chile: Evidencia científica para la toma de decisiones. Informe de   la   mesa   de   Biodiversidad.   Santiago:   Comité   Científico   COP25; Ministerio de Ciencia, Tecnología, Conocimiento e Innovación.).. Because of this, there is a need to incorporate different components of ecological knowledge as well the interaction with local communities in these PA in order to generete projections of climate chage to develop conservation plans to the future.

This review revist the ecological literature carry out in these three protected areas and its surroundings in Los lagos Region in order to generate a base line that allow to proyect scenarios of climate change to systematic conservation planning in PA.

4. Describe the present paper 

We made a systematic review of research in the Web of Knowledge database searching by the names of the three PA: PNP, VPRNP, and AANP; andby the greographical area of Southern Chile.
Doing so, we were able to identified tendencies and gaps in research developed in these three National Parks. We could defined a vision on where to focus new studies that allow systematic conservation plans that includes information to deal with climate change and ensure the biological diversity in Southern Chile.

incluir: possibility to generate a methodology to include climate Change into PAs planning, from their creation to their management and administration, assessing their value as well as their vulnerabilities at landscape scales


# Methodology

1. Overview-purpose of the work-give source of material/equipment used 
[General overview of this section]
In order to identify research developed in the focus area, a systematic review of literature was performed through the Web of Science database. Information was categorized according to research areas presented in this project.

[Provide background information and justification]
We focus our systematic review geographicaly in the Andes mountain chain and central vally, and not coastal mountain chain and coast.

[Provide an overview of the procedure/method itself]
Two eligibility criteria were performed: 1. including the name of the National Parks of interes, using keywords at topic level: "Puyehue National Park" or "Vicente Perez Rozales National Park" or "Alerce Andino National Park", and 2. Geographic areas surrounding the National Parks, using keywords at topic level: "South Central Chile" or "North Chilean Patagonia" or "Los Lagos Region". The period of the search included from 1975 until October 2020. Selection of articles followed prisma flow diagram. Grey-literature was not incorporated in the selection.

2. Details about materials and methods- justify choices 
[Provide details about what was done and used and shows that care was taken] 
Articles selected were categorized by publication year, source title, keywords used, area of study, study location, objective, methodology, process, and study object. 

[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
Area of study included Archaeology & Paleoecology, Climate & environment, Ecosystem functioning & services, Freshwater biodiversity, Hydrology, Social-ecology, and Species & distribution.

Study location encompas categories such as the three National Parks of interest: AANP, PNP, and  VPRNP; adjacents areas to NP: Adjacent to AANP, Adjacent to PNP, Adjacent to VPRNP; similar ecosystems to NP:  Andes of Los Rios Region, Argentinian andes, and Neuquen in Argentina; Larger areas that comprise NP: Los Lagos Region, 2 regions, 3 regions, 4 regions,  5 regions, More than 5 regions; Global studies: Chile, Chile & Argentina; and Close urban centers: Valdivia

[Methodology classified according to how data was obtain]
The category called proccess implies biological, ecological or physical  

3. Relate to other studies 
[Describe what was done by referring to existing mehods in the literature] 
We focus our findings in Los Lagos región research and andean studies, leaving out coastal systems and in particular Chiloe island.

[Provide more detailed information about the method and show that was a good choice]

4. Indicate where problems occurred 
[Mention possible difficulty in the methodology]

# Results

1. Revisting the research aim/existing research
2. General overview of results
A total of  `r nrow(DF)` articles were selected in this review. From those `r (DF %>% dplyr::filter(Keywords.used=="Name of parks") %>% nrow())` articles were find from National parks names searching and `r (DF %>% dplyr::filter(Keywords.used =="Close area") %>%  nrow())` articles from searching nearby areas od the parks. 

3. Invitations to view results
In general terms, articles have been growing in number, however there are years that clearly show a decline in publications (Fig \@ref(fig: Years)). 


```{r Years}
Pub_year <-ggplot(DF) + geom_bar(aes(x = Publication.Year))+  labs(y="Number of articles", x="Publication year")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))
Pub_year
```



From the total of articles, only `r (((DF %>% dplyr::filter(Study.location %in% c("AANP", "PNP", "VPRNP")) %>% nrow())/nrow(DF))*100)` % where carry ount in the National parks of interest (Fig \@ref(fig: Locations)). `r (DF %>% dplyr::filter(Study.location == "PNP") %>% nrow())` articles were carry out in PNP, and only `r (DF %>% dplyr::filter(Study.location == "AANP") %>% nrow())` in AAPN and `r (DF %>% dplyr::filter(Study.location == "VPRNP") %>% nrow())` in VPRPN.
Adjacents areas to NP comprehended a `r ((DF %>% dplyr::filter(Study.location %in%  c("Adjacent to PNP", "Adjacent to AANP", "Adjacent to VPRNP")) %>% nrow())/nrow(DF)*100)` % of the studies. 





```{r Locations}
DF_Location <- DF %>%  group_by(Study.location) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(Study.location)) %>% 
  mutate(Study.location=fct_reorder(Study.location, -n))

DF_Location2 <- DF_Location %>% 
  mutate(Study.zone= case_when(Study.location %in% c("PNP", "AANP", "VPRNP")~"National Parks", 
                               Study.location %in% c("Adjacent to PNP", "Adjacent to AANP", "Adjacent to VPRNP")~"Adjacent areas to NP", 
                               Study.location %in% c("Andes of Los Rios Region", "Neuquen, Argentina", "Argentinian andes")~"Similar ecosystems", 
                               Study.location %in% c("Los Lagos Region", "2 regions","3 regions", "4 regions", "5 regions", "More than 5 regions")~"Larger areas that comprise NPs", 
                               Study.location %in% c("Chile", "Chile and Argentina")~"Global studies",
                               Study.location %in% c("Valdivia")~"Close urban center")) %>%
  mutate(Study.zone= str_wrap(Study.zone, 15))
                                
Location2 <-ggplot(DF_Location2, aes(x = fct_reorder(Study.zone,n, .desc=TRUE), y = n, group = Study.location)) + geom_col(aes(fill=Study.zone), position="dodge", color="black") + geom_text(aes(label =Study.location), size=4, position=position_dodge(0.9), angle=90,vjust=0.5, hjust=-0.04 ) + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,66))+theme(legend.position = "none")+ scale_fill_brewer(palette = "Dark2") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
Location2
```


Most of the study areas ar mention in less than 20 articles in this revision, however ecosystem functionning and services highlights with its number of articles published ` r ((DF %>% dplyr::filter(Area.of.study=="Ecosystem functioning and services") %>% nrow() )/nrow(DF) )*100` % of the total (Fig \@ref(fig: Areas)). Ecosystem functionning and services has been studied in the three NP, however its proportion in PNP is notably higher than the other NP.

```{r Areas, fig.height=10, fig.width=8}
DF_Area <- DF %>% 
  mutate(Area.of.study2= case_when(Area.of.study %in% c("Arqueological","Paleoecology" )~"Archaeology and Paleoecology",
                                          Area.of.study %in% c("Climate","Environmental conditions", "Seismiology" )~ "Climate and environment",
                                          Area.of.study %in% c("Biogeography","Species", "Exotic species" )~ "Species and distribution",
                                          Area.of.study %in%  "Ecosystem functioning and services" ~ "Ecosystem func. & servic.",
                                          Area.of.study %in% "Freshwater biodiversity" ~ "Freshwater biodiversity",
                                          Area.of.study %in% "Hydrology" ~ "Hydrology",
                                          Area.of.study %in% "Social-ecological" ~ "Social-ecology")) %>% 
  mutate(Area.of.study2= str_wrap(Area.of.study2, 15)) %>% 
  group_by(Area.of.study2) %>% summarise(n = n()) %>% ungroup() %>%
   dplyr::filter(!is.na(Area.of.study2))

p1 <-ggplot(DF_Area) + geom_col(aes(x = fct_reorder(Area.of.study2, desc(n)), y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle =90, vjust = 0.5, hjust=1)) 


DF_Area2 <- DF %>% dplyr::filter(Study.location %in% c("PNP", "VPRNP", "AANP")) %>% 
   mutate(Area.of.study2= case_when(Area.of.study %in% c("Arqueological","Paleoecology" )~"Archaeology and Paleoecology",
                                          Area.of.study %in% c("Climate","Environmental conditions", "Seismiology" )~ "Climate and environment",
                                          Area.of.study %in% c("Biogeography","Species", "Exotic species" )~ "Species and distribution",
                                          Area.of.study %in%  "Ecosystem functioning and services" ~ "Ecosystem func. & servic.",
                                          Area.of.study %in% "Freshwater biodiversity" ~ "Freshwater biodiversity",
                                          Area.of.study %in% "Hydrology" ~ "Hydrology",
                                          Area.of.study %in% "Social-ecological" ~ "Social-ecology")) %>% 
  mutate(Area.of.study2= str_wrap(Area.of.study2, 15)) %>% 
  group_by(Area.of.study2, Study.location) %>% summarise(n = n()) %>% ungroup() %>%
   dplyr::filter(!is.na(Area.of.study2))
  

p2 <- ggplot(DF_Area2) + geom_col(aes(x = fct_reorder(Area.of.study2, desc(n)), y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + facet_wrap(~Study.location, scales="free_x")

p1/p2
```


Data collected form the field is abundant  ` r ((DF %>% dplyr::filter(Mehodology %in% c("Field survey", "Field collection", "Field experiment")) %>% nrow() )/nrow(DF) )*100` % (Fig \@ref(fig: Areas)).

```{r}
DF <- DF %>% 
  mutate(General_methods= case_when(
    Methodology %in% c("Field collection", "dendrochronology", "Electric fishing")~"Field collection",  
    Methodology %in% c("Field survey", "Sampling stations")~"Field survey", 
    Methodology %in% c("Field experiment", "Transplant experiment", "Seedling experiment", "Stratigraphy")~"Field experiment", 
    Methodology %in% c("Communicational strategy", "Discussion", "Quantitative and qualitative methods", "Survey", "Interview")~"Social methods", 
    Methodology %in% c("Correlations","Modeling", "Multivariate model", "Remote sensing","Simulations", "spatially explicit model")~"Modeling", 
    Methodology %in% c("Chile", "Chile and Argentina")~"Global studies",
    Methodology %in% c("Isotopes","Genetic analysis", "Reconstruction of mtDNA")~"Molecular analysis",
    Methodology %in% c("Review of literature")~"Review of literature"))

#DF_Methodology <- DF %>%  group_by(Methodology, General_methods) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(Methodology)) %>% mutate(Methodology=fct_reorder(Methodology, -n)) %>% mutate(General_methods= str_wrap(General_methods, 13))

#p1 <-ggplot(DF_Methodology, aes(x = fct_reorder(General_methods, n, .desc=TRUE), y = n, group = Methodology)) + geom_col(aes(fill=General_methods), position="dodge", color="black") + geom_text(aes(label =Methodology), size=4, position=position_dodge(0.9), angle=90,vjust=0.5, hjust=-0.04 ) + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,66))+theme(legend.position = "none")+ scale_fill_brewer(palette = "Dark2") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
#p1
DF_Methodology2 <- DF %>%  group_by(General_methods) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(General_methods)) %>% mutate(General_methods=fct_reorder(General_methods, -n)) %>% mutate(General_methods= str_wrap(General_methods, 13))

p2 <-ggplot(DF_Methodology2, aes(x = fct_reorder(General_methods, n, .desc=TRUE), y = n)) + geom_col(position="dodge", color="green") + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,35))+theme(legend.position = "none") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
p2


```
Field collection included mehods sucha asdendrochronology, electric fishing.


Modeling category included correlational, multivariete , and spatially explicit models





```{r}
DF_object <- DF %>%  group_by(Study.object) %>% summarise(n = n()) %>% ungroup() %>% dplyr::filter(!is.na(Study.object)) %>% mutate(Study.object=fct_reorder(Study.object, -n))

DF_object <- DF_object %>% 
  mutate(General_object= case_when(
    Study.object %in% c("People", "Urban areas")~"Human",  
    Study.object %in% c("Aegorhinus", "Austrocedrus", "Bird species","Chusquea", "Craspedacusta","Didymosphenia", "Dromiciops", "F. cupressoides", "Lichen", "Nothofagus",   "Salmonids", "Liolaemus", "Wild boar")~"Species", 
    Study.object %in% c( "Groundwater Storage", "Lakes", "runoff", "Soil","Streams", "watershed")~"Geographic elements", 
    Study.object %in% c("Forest","Native forest")~"Ecosystem",
    Study.object %in% c("Fires","Particulate matter","Precipitation", "Rock art")~"Physical conditions",
    Study.object %in% c("Aquatic plants" )~"Group of plants",
    Study.object %in% c("Bird species","Fishes","Crustacean", "Evergreen trees", "Nothofagus")~"Communities")) %>%
  mutate(General_object= str_wrap(General_object, 18))


p1 <-ggplot(DF_object, aes(x = fct_reorder(General_object, n, .desc=TRUE), y = n, group = Study.object)) + geom_col(aes(fill=General_object), position="dodge", color="black") + geom_text(aes(label =Study.object), size=4, position=position_dodge(0.9), angle=90,vjust=0.5, hjust=-0.04 ) + labs(y="Number of articles", x="Study locations")  + theme_classic()+ ylim(c(0,66))+theme(legend.position = "none")+ scale_fill_brewer(palette = "Dark2") + theme(text=element_text(size=18,  family="Times"), axis.text.x = element_text(angle = , vjust = 1, hjust=1))
p1


```


4. Specific/key results in details


## Hydrology

From the total of articles centered on hydrology, 

```{r Hydrology, fig.height=7, fig.width=10}
DF_Hydro <- DF %>%  group_by(Area.of.study, Process, General_methods, Study.object) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(Area.of.study== "Hydrology")
#%>% mutate(Area.of.study= str_wrap(Area.of.study, 24)) %>% dplyr::filter(!is.na(Area.of.study))

Hydro1 <- ggplot(DF_Hydro) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Hydro2 <- ggplot(DF_Hydro) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Hydro3 <- ggplot(DF_Hydro) + geom_col(aes(x = Study.object, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5)) 
(Hydro1 + Hydro2)/Hydro3
```

Spectral characterrization and comparison among lakes in @delosRiosSpectral
We show that annual runoffis highly sensitive to the relative area of FPto NF: ratios of FP to NF areas of 10%, 50% and 90% would lead to 3%,−18% and−40% changes inmean annual runoff, respectively.(Alvarez-Garreton et al 2019)



## Ecosystem functioning and services

Field collection methods registered in ecosystem functioning and services included activities such as dendrochronological samples, 
Field surveys methods area a lot
Field experiment methods included seedling and transplant experiments.



```{r Ecosys, fig.height=7, fig.width=9}
DF_Ecosys <- DF %>%  group_by(Area.of.study, Process, General_methods, Study.object) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(Area.of.study== "Ecosystem functioning and services")
#%>% mutate(Area.of.study= str_wrap(Area.of.study, 24)) %>% dplyr::filter(!is.na(Area.of.study))

Ecosys1 <- ggplot(DF_Ecosys) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Ecosys2 <- ggplot(DF_Ecosys) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Ecosys3 <- ggplot(DF_Ecosys) + geom_col(aes(x = Study.object, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
(Ecosys1 + Ecosys2)/Ecosys3
```

Chusquea fenology in @delaFuenteChusquea 
El área de estudio se ubica en el sector de Antillanca (40º78’S y 72º22’O,

Improvements for the study of volcanic activity [@AmoebaeTephra]

Steam radious of F. cupressoides and the determination of environmental variables that affect its growth... with projections in climate change [@Stem_F]

SUcculence in rain forest [@GodoySucculence]
Key results – We show that leaves from sun conditions, the environment with higher water demand, have lower SLA (specific leaf area), thicker epidermis and store more water due to a thicker spongy parenchyma, than leaves from shade conditions. Conclusions  –  We  found  high  phenotypic  variation  in  S.  repens at intraspecific level in response to contrasting environmental conditions. This variation reflects a two-fold strategy common in epiphytes: increase water storage and reduce water loss. Furthermore, it suggests that leaf succulence has an adaptive value even in a temperate cold rainforest. We discuss that the occurrence of succulence on a cold rainforest might be explained by a combination of ecological, biogeographic and phylogenetic factors.

macropytes  and  riparian  assemblages  are  not  random,  that means  that  the  regulator  factors  are  deterministic. 


They reconstructed stand development on sites affected by these disturbances (complex mosaic of disturbance patterns, including the effects of the strong 1960 earthquake as well as fire and wind disturbance), and compared these patterns with the structure of old-growth forests along an elevation gradient from species-rich montane rain forest to mono-typic subalpine Nothofagusforests


## Social-ecological
Socio-ecological research included quantitative and qualitative social methods which includes people's surveys, interviews and articles of discission based on etnography.


```{r Social, fig.height=9}
DF_Social <- DF %>%  group_by(Area.of.study, Process, General_methods, Study.object) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(Area.of.study== "Social-ecological")
#%>% mutate(Area.of.study= str_wrap(Area.of.study, 24)) %>% dplyr::filter(!is.na(Area.of.study))

Social1 <- ggplot(DF_Social) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Social2 <- ggplot(DF_Social) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Social3 <- ggplot(DF_Social) + geom_col(aes(x = Study.object, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5)) 
(Social1 + Social2)/Social3
```

Turism and peoples movement in @SozaAmigoTurism

conection with PNP with thre cities valdivia, Osorno y Puerto Montt (154.716, 147.826, and 220.143 of urban population respectibly, according to 2017 Census, Chile )
The results show that the chang-es in the economic structure had improve the main sectors of the centers, weakening the potential development of the Park. Especially the lacks of connectivity development and the small supply of good and services of the Park are the main constraint that arise from the analysis to increase the number and length of visits. 


Social actors in AANP and LLNR buffer in @mardones_social

The study was focused in the buffer zone 
El estudio combina el análisis cualitativo del mapeo de actores (MDA) con el mé-todo cuantitativo del análisis de redes sociales (ARS).
La inves-tigación utiliza una aproximación sociométrica al análisis de redes sociales, el cual se refiere al estudio de las propiedades estructurales de una red, tales como densidad y cohesión (Marín, Gelcich, Castilla, & Berkes, 2012). 
Social studies mention haigh fragmentations of social network according to economic sectors (agriculture, artisal fisheries, turism, among others ). 
Low participation and separation from the protected area which has not incorporated the community 


## Freshwater biodiversity

Field collection methods registered in freshwater biodiversity included activities such as electric fishing and sampling stations.

```{r Fresh, fig.height=9}
DF_Fresh <- DF %>%  group_by(Area.of.study, Process, General_methods, Study.object) %>% summarise(n = n()) %>% ungroup() %>%
  dplyr::filter(Area.of.study== "Freshwater biodiversity")
#%>% mutate(Area.of.study= str_wrap(Area.of.study, 24)) %>% dplyr::filter(!is.na(Area.of.study))

Fresh1 <- ggplot(DF_Fresh) + geom_col(aes(x = Process, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Fresh2 <- ggplot(DF_Fresh) + geom_col(aes(x = General_methods, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
Fresh3 <- ggplot(DF_Fresh) + geom_col(aes(x = Study.object, y=n)) +labs(y="Number of articles", x=" ")  + theme_classic()+   theme(text=element_text(size=18,  family="Times"))+ theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust=0.5)) 
(Fresh1 + Fresh2)/Fresh3
```


## Conservation priorization -Climate change

5. Comparisons with results in other research
6. problems with results

Projections: Climate change in time


7. Possible implications with results

# Discussion 

1. Revisting previous research- summarise 
[Revisit previous research] 
The area of study that includes the tree national parks has been modified by continuos natural events such as volcanic activity, with  volcanic centers such as Puyehue (2,240 m in PNP), Cordón Caulle (2,236 m; in PNP), Tronador (3,565 m; in VPRNP), Osorno (2,661 m; López-Escober et al., 1992; Petit-Breuilh, 1999) [@SternVolcanism], and earthquakes as Valdivia in 1960.  (https://www.nature.com/articles/s41467-018-05989-6)


[Revisit Introduction to recall specific weakness in methodology used in previous studies]
no hay estudios en cambio climatico y se ncesesita saber que hay para poder preparse para el cambio climatico


2. Mapping 
[Revisit methodology used in this study] 
Review of literature in 

[Revisit and summarise the results] 
Studies were focussed in ecosystems functioning and services with special developed in forestry aspects such as growth, sucession and regeneration, showing a bias in forestry economical potential of native forest.
there is a gap in social-ecological studies that includes local comunities perceptions of national parks and their relationship in terms of interactions.

[Show where and how the present work fits into the research “map” in this field]


3. Achivements/contributions- refining implications 
COSAS ENCONTRADAS EN EL REVIEW POR AREA: QUE SE HA HECHO Y LO BUENO DE ESO

[Recall an aspect of the results that represents a postitive achievement or contribution of this work] 
This review allow to recognize the studies carry out in these three national parks and the research in the area in theirs surroundings

[Focus in the meaning and implications of the achievements in this work]

[Note if one of the achievement or contributions of the work is a novelty] 

[Describe implications of the results, including possible applications]
These knowledge allow to generate a baseline to work in the future

4. Limitations-current and future work-applications 
COSAS QUE FALTAN EN CADA AREA Y QUE LIMITA ESA FALTA DE CONOCIMINETO
TOMANDO EN CONSIDDERACION ESTA INFORMACION SE PUEDE ARMAR UNA PROYECCION MAS CABAL DE LOS EFECTOS DEL CAMBIO CLIMATICO

[Describe limitations which should direct future research] 
Socio-ecological studies should contemplate that there is a sentiment described in local sociology studies describing provinces in this region do not share a common notion of territory or a regional common agenda. This has been explain as cultural changes as a product of economic activities such as salmoniculture, where the dependency of international markets predominates (Montecinos, 2009, p. 24).


[Suggest a specific area to be addressed in future work]


Latitudinal patterns in plant biodiversity [@BanisterLatitudinal] shows 
at 40°S there are more than 800 species, based on a bibliographic review of existing floristic studies at 2012.

There is a gap in fire studies even when the region present an important area in forestry plantations.
this is important because the structure and composistion of forest plantations promotes more fires than native forest of Nothofagus (Gómez-González et al., 2019; McWethy et al., 2018).

Fire events in similar areas (low access, topography, and climate) have covered large areas and affected native ecosystems. Fires in Parque Nacional Torres del Paine en 2012 (cerca de 17.000 ha), Reserva Nacional China Muerta de 2015 (cerca de 3.700 ha) y Colonia Sur, Cochrane en 2019 (cerca de 15.000 ha) were very difficult to control (Arroyo, M. T. K., A. Pauchard, D. Alarcón, J. Armesto, F. Bozinovic, R. Bustamante, C. Echeverría, S. A. Estay, R. A. García, A. Gaxiola, M. Mi-randa, P. Pliscoff, D. Rozas, C. Salas-Eljatib y R. Rozzi (2019). «Impactos del cambio climático en la biodiversidad y las funciones ecosistémicas en Chile». En P. A. Marquet et al. (editores), Biodiversidad y cambio climático en Chile: Evidencia científica para la toma de decisiones. Informe de la mesa de Biodiversidad. Santiago: Comité Científico  COP25; Mi-nisterio de Ciencia, Tecnología, Conocimiento e Innovación.)





There are just a few studies in hydrology in the region, although there are some more characterization including the valdivian forest [@LittleWatershed].

freshwater: we did not consider dideases in in chilean salmon industry [@RozasAmoebic]

Although we contemplate andean studies here, volcanic activity could create microhabitats more similar to areas in another region or with another climate ???
Remarkably consistent thermal state [@RotmanThermal]

plantas de embotrium y actividad volcanica [@DelgadoEmbothrium]
plant invasion in Climatic and socio-economic factors determine thelevel of invasion by alien plants in Chile [@FuentesInvasion]

Comparative morphology of annual shoots in seedlings of five Nothofagus species from Argentinian patagonia [@RaffaeleMorphology]

A Multiscale Method for AssessingVegetation Baseline of Environmental [@PauchardMultiscale]






### References